---
title: "DSS Computing Bootcamp Template"
author: "Woo Min Aiden Kim"
<<<<<<< HEAD
date: "8/25/2016"
=======
date: "8/26/2016"
>>>>>>> e8fea228809ad1ab11e1debef020259145daa07a
output: html_document
---

## Load packages

Load the following packages for 

- data wrangling (`dplyr`), and 
- data visualizaiton (`ggplot2`)

```{r message=FALSE}
library(dplyr)
library(ggplot2)
```

## Load data

```{r}
gap_upd <- read.csv("https://bit.ly/gap_data_upd")
```

## Exercises

### Exercise 1

How many observations are in this dataset?

```{r nrow, echo=FALSE}
n <- nrow(gap_upd)
```
There are `r n` observations in the dataset


### Exercise 2

Visualize the relationship between GDP and life expectancy for 
countries in Europe in 1952 using a scatter plot.

```{r eu_52}
eu_52 <- gap_upd %>%
  filter(continent == "Europe", year == 1952)
ggplot(data = eu_52, aes(x = gdpPercap, y = lifeExp)) +
  geom_point()  
```

### Exercise 3

Add year 1967 in another color.

```{r eu_52_67}
eu_5267 <- gap_upd %>%
  filter(continent == "Europe", year %in% c(1952, 1967))

ggplot(data = eu_5267, aes(x = gdpPercap, y = lifeExp, color = (year))) +
  geom_point()
```

